DMRGenie: Graphical interface for entanglement renormalization

### 2025-12-03 paper/paper.tex
Update paper.tex

Quantum information methods have become a tantalizing path to creating new algorithms and methods. These range from quantum algorithms implemented on quantum computers \cite{nielsen2010quantum} (but since no perfect quantum computer exists as of yet, so simulations with classical methods are still required) to entanglement renormalization techniques.\footnote{This class of methods is more commonly referred to as tensor networks, simply, but with the rise of machine-learning and other methods particularly in quantum chemistry that are formulated on tensor networks, a distinguishing name is required. We choose to expand the usage of the term from Ref.~\cite{vidal2007entanglement} since all methods are fundamentally optimizing over quantities relevant for quantum information ({\it i.e.}, the entanglement) and renormalization was originally introduced to describe this class of methods \cite{wilson1983renormalization,krishna1980renormalization}. The methods required to implement an algorithm in this context is different from other contexts, notably machine learning.}

@@

Realistically, only about a rank-14 tensor can be represented on a laptop machine. This is because each of the tensor indices has dimension of at least two, approaching the memory limitations of these devices. Therefore, the rank of the tensors represented here are small and often only a few indices are present.

@@

Building these algorithms from a purely diagrammatic level is a desirable possibility. This opens the possibility to using a graphical user interface to denote the various steps in the implementation of the entanglement renormalization algorithms

@@

For example, if the user wanted to input a Heisenberg Hamiltonian of 
\begin{equation}\label{heisMPO}
\hat H = -J\sum_{i} \left( \sigma^x_i \sigma^x_{i+1} + \sigma^y_i \sigma^y_{i+1} + \sigma^z_i \sigma^z_{i+1}\right)
\end{equation}
where $J$ is the Hamiltonian constant, then it would be possible to do so term by term. An example of the input is given in Fig.~\ref{heismodel}.

>>>>

Quantum information methods have become a tantalizing path to creating new algorithms and methods. These range from quantum algorithms implemented on quantum computers \cite{nielsen2010quantum} to entanglement renormalization techniques.\footnote{This class of methods is more commonly referred to as tensor networks, simply, but with the rise of machine-learning and other methods particularly in quantum chemistry that are formulated on tensor networks, a distinguishing name is required. We choose to expand the usage of the term from Ref.~\cite{vidal2007entanglement} since all methods are fundamentally optimizing over quantities relevant for quantum information ({\it i.e.}, the entanglement) and renormalization was originally introduced to describe this class of methods \cite{wilson1983renormalization,krishna1980renormalization}. The methods required to implement an algorithm in this context is different from other uses, notably machine learning.}

@@

%Realistically, only about a rank-14 tensor can be represented on a laptop machine. This is because each of the tensor indices has dimension of at least two, approaching the memory limitations of these devices. Therefore, the rank of the tensors represented here are small and often only a few indices are present.

@@

Building these algorithms from a purely diagrammatic level would be useful. This opens the possibility to using a graphical user interface to denote the various steps in the implementation of the entanglement renormalization algorithms.

@@

For example, if the user wanted to input a Heisenberg Hamiltonian of 
\begin{equation}\label{heisMPO}
\hat H = -J\sum_{i} \left( \hat S^x_i \hat S^x_{i+1} + \hat S^y_i \hat S^y_{i+1} + \hat S^z_i \hat S^z_{i+1}\right)
\end{equation}
where $J$ is the Hamiltonian constant, then it would be possible to do so term by term. An example of the input is given in Fig.~\ref{heismodel}.
